### 2017-01-08 paper/evaluation.tex
Added CPU isolation

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }\emph{git} to fetch
subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test
subjects. Our evaluation scripts depends on \emph{Python 3.4} and
\emph{Bash} to execute.  For replication, all source artifacts are
publicly available at \Fix{create gh-pages}, including supporting
scripts (\eg, the script that test subjects and generates the raw
data), and the full list of projects. \Comment{, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  To avoid noise from
operating system events, we used a dedicated server remotely via SSH
with the operating system running only essential services (\eg, the
SSH server). In addition, we \Fix{describe CPU isolation with Kernel
settings}.

>>>>

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS
Trusty Tahr} (64-bit version). Software settings include \Comment{the
Linux \emph{sysstat} package to measure performance, }\emph{git} to
fetch subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test
subjects. Our evaluation scripts depends on \emph{Python 3.4} and
\emph{Bash} to execute.  For replication, all source artifacts are
publicly available at \Fix{create gh-pages}, including supporting
scripts (\eg, the script that test subjects and generates the raw
data), and the full list of projects. \Comment{, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  To avoid noise from
operating system events, we used a dedicated server remotely via SSH
with the operating system running only essential services (\eg, the
SSH server). In addition, we configured the \CodeIn{isolcpus} option
from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
to execute our experiment and the remaining CPUs to run the operating
system. By isolating a set of virtual CPUs, we prevent
context-switching from the experiment processes and OS-related
process.
